\subsection{Notes from meeting 24/10/2012}

Amanda was not present for this meeting.

\subsection{Discussed}

\begin{itemize}
\item
  We discussed the PDF conversion routine and decided that whilst
  important, it is crucial not to get too caught up in this.
\item
  Maria is going to send me a link to an existing PDF to XML converter
  that might provide the functionality with some tweaking - or at least
  help
\item
  We discussed the Python version of Sapienta which currently supports
  SciXML and simplified versions thereof.
\item
  Maria needs to send me a couple of data files for this to work
  properly.
\item
  Confirmed that Jerboa is a Java library (I was confused because I was
  expecting a python toolkit) and need to look at it properly now.
\item
  Discussed the actual functionality of the system and came up with a
  brief system outline, around which I can plan.
\end{itemize}

\subsection{TODO}

\begin{itemize}
\item
  Now that we know what the system is going to do (See System Outline), I need to look at features that
  will allow us to:
\item
  Pre-classify documents based on their topic, type, result etc
\item
  Determine document similarity based on user preference from their
  tagging etc. (I can make use of the ``Features in sentiment analysis''
  paper for this)
\item
  Run more tests on the PDF parser and potentially look at another
  solution if this takes up too much time.
\item
  Have a go with Python SAPIENTA once the data models are present
\end{itemize}
